Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-05-03 2016-Weak-FH-Bisim/WeakBisim.tex
suite lemma

\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}

@@

Note that we added  the substitution $\subst{\Post_{OT_x}}$ on the right side of the implication without affecting the validity of the statement, because of the domain independence of the substitution. Hence a little rewriting gives:\\

@@

By replacing the inner sub-term $(\Pred_{s_{11},t_x}\wedge\Pred_2)$ by the conclusion of the corresponding implication given in case 2,  the formula becomes: \\

@@

   ( \forall j\in J_{x y}. \vis{\beta_{2j}}\!\!=\!\!\gamma_{jx y}\Rightarrow\\~~\qquad\quad \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y}\! \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_{OT_{x y}}})\Big)\subst{\Post_1\shortotimes\Post_{OT_x}} \Big)$\\

@@

\Big(\forall j\in J_x. \vis{\beta_{1j}}\!\!=\!\!\gamma_{jx} \land  \forall j \in J_{x y}. \vis{\beta_{2j}}\!\!=\!\gamma_{jx y}\Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \\\subst{\Post_1\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\shortotimes \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\ 

@@

\Big(\forall j\in J_x.\vis{\beta^1_j}\!=\!\gamma_{jx} \land  \forall j \in J_{x y}. \vis{\beta_{2j}}\!=\!\gamma_{jx y} \Rightarrow \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \alpha_x\!=\!
\tau \land \alpha\!=\! \alpha_{x y} \land (\Pred_{s_{21},t_{xy}} \land  \Pred_3) \subst{\Post_2\shortotimes \Post_1\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\ 
Again note that because of the domain independence of the substitution, we deleted $\subst{\Post_1}$, and  we  added  $\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}$ on the right side of the implication.\\

Finally, by replacing $(\Pred_{s_{21},t_{xy}} \land  \Pred_3)$
by the conclusion of the corresponding implication given in case 3, we get:\\
$(\Pred_{s,t} \land \Pred_1)\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
\Big(\forall j\in J_x.\vis{\beta_{1j}}\!\!=\!\!\gamma_{jx} \land\!  \forall j \!\in\! J_{x y}.\vis{\beta_{2j}}\!\!=\!\!\gamma_{jx y} \forall j\!\in\! J_{x y z}. \vis{\beta_{3j}}\!\!=\!\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\!\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!
\tau \!\land \alpha\!=\!\alpha_{x y} \land \alpha_{x y z}\!=\!\tau \land \Pred_{s_{31},t_{x y z}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\shortotimes \,\Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$

Therefore, having $s_{31}=s'$ we can conclude:\\
$(\Pred_{s,t} \land \Pred_1)\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
\Big(\forall j\in J_{x y z}. \vis{\beta^1_j}.\vis{\beta_{2j}}.\vis{\beta_{3j}}\!=\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha\!=\!\alpha_{x y} \land \Pred_{s',t_{x y z}}\subst{\Post_{OT}\shortotimes\Post_{OT_{x y z}}\shortotimes\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$
This is exactly what we needed to prove. \qed
\end{proof}

>>>>

\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}}\displaystyle{\bigvee_{z\in Z}}

@@

Note that  on the right side of the implication we added  the substitution  of $\Post_{OT_x}$ without affecting the validity of the statement, because of the domain independence of the substitution \TODO{l'argument ne me convainc pas}. Hence a little rewriting gives:\\

@@

By replacing the inner sub-term $(\Pred_{s_{11},t_x}\wedge\Pred_2)$ by the conclusion of the  implication given in case 2,  the formula becomes: \\

@@

   ( \forall j\in J_{x y}. \vis{\beta_{2j}}\!\!=\!\!\gamma_{jx y} \\ \Rightarrow \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y}\! \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_{OT_{x y}}})\Big)\subst{\Post_1\shortotimes\Post_{OT_x}} \Big)$\\

@@

\Big(\forall j\in J_x. \vis{\beta_{1j}}\!\!=\!\!\gamma_{jx} \land  \forall j \in J_{x y}. \vis{\beta_{2j}}\subst{\Post_1\shortotimes\Post_{OT_x}} \!=\!\gamma_{jx y}  \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_1\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \subst{\Post_1\shortotimes\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\shortotimes \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\ 
As $Post_1$  does not act on $\gamma_{jx y}$, nor on $ \Pred_{OT_{x y}}$ and $  \alpha_{x y}$, the formula can be simplified as follows:\\
\Big(\forall j\in J_x. \vis{\beta_{1j}}\!=\!\gamma_{jx} \land  \forall j \in J_{x y}. \vis{\beta_{2j}}\subst{\Post_{OT_x}}\!=\!\gamma_{jx y}   \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \subst{\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\shortotimes \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\ 

@@

\Big(\forall j\in J_x.\vis{\beta^1_j}\!=\!\gamma_{jx} \land  \forall j \in J_{x y}. \vis{\beta_{2j}}\subst{\Post_{OT_x}} \!=\!\gamma_{jx y} \Rightarrow \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \alpha_x\!=\!
\tau \land \alpha\!=\! \alpha_{x y} \subst{\Post_{OT_x}} \land (\Pred_{s_{21},t_{xy}} \land  \Pred_3) \subst{\Post_2\shortotimes \Post_1\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\ 
Again note that because of the domain independence of the substitution, we removed $\Post_1$ and  we  added  $\Post_{OT_{x y}}\shortotimes\,\Post_{OT_x}$ on the right side of the implication.\\
Finally, by replacing $(\Pred_{s_{21},t_{xy}} \land  \Pred_3)$
by the conclusion of the  implication given in case 3, we get:\\
$(\Pred_{s,t} \land \Pred_1)\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\\
\hspace{1cm} \implies\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
\Big(\forall j\in J_x.\vis{\beta_{1j}}\!=\!\gamma_{jx} \land\!  \forall j \!\in\! J_{x y}.\vis{\beta_{2j}}\subst{\Post_{OT_x}}\!=\!\gamma_{jx y}   \land \\
 \forall j\!\in\! J_{x y z}. \vis{\beta_{3j}} \subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \!=\!\gamma_{j x y z}  \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}} \subst{\Post_{OT_x}} \land \\
  \Pred_{OT_{x y z}}\!\subst{\Post_{OT_{x y}}\shortotimes\,\Post_{OT_x}} \land \alpha_x\!=\!
\tau \!\land \alpha\!=\!\alpha_{x y} \subst{\Post_{OT_x}}\land \alpha_{x y z}\!=\!\tau \land \Pred_{s_{31},t_{x y z}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\shortotimes \,\Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\
Having $s_{31}=s'$ we can conclude:\\
$(\Pred_{s,t} \land \Pred_1)\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
\Big(\forall j\in J_{x y z}. \vis{\beta^1_j}.\vis{\beta_{2j}}\subst{\Post_{OT_x}}.\vis{\beta_{3j}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \!=\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha\!=\!\alpha_{x y}\subst{\Post_{OT_x}} \land \Pred_{s',t_{x y z}}\subst{\Post_{OT}\shortotimes\Post_{OT_{x y z}}\shortotimes\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\
 \TODO{gamma ne me convainc pas et je dois generaliser}
This is exactly what we needed to prove. \qed
